---
title: "Working with Air Force Specialty Codes (AFSCs) in R"
author: "Brandon M. Greenwell"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Installation

```{r, message=FALSE}
# Install development version from GitHub (requires devtools package)
devtools::install_github("bgreenwell/afsc")

# Load package
library(afsc)

# List all the objects in the afsc package
ls("package:afsc")
```

## Basic pattern analysis
The first two are enlisted AFSCs, the latter contains a prefix and suffix (both of which are optional). The second two are officer AFSCS, the first of which contains a prefix. The last four are not valid AFSCs; the last one is an AFSC, but has been entered incorrecltly (it has aan extra whitespace and the letter is lowercase).
```{r}
afscs <- c("X1N371E", "9T000", "T63A3", "63A3", "ABCDE", NA, "", " 63a3")
unique_patterns(afscs, as_table = TRUE)
```

Only four of the patterns match those of an enlisted or officer AFSC. 

## Checking AFSCs for correctness

```{r}
is_valid_afsc(afscs)
```

```{r}
get_valid_afscs(afscs)
get_invalid_afscs(afscs)
```

```{r}
is_enlisted(afscs)  # logical vector
is_officer(afscs)  # logical vector
afsc_type(afscs)  # character vector
```

## Extracting different AFSC components

```{r}
get_prefix(afscs)
get_suffix(afscs)
```
